\input{title.tex}

### 2022-04-06 docs/papers/01_manuscript/03_causes.tex
docs(results2-section1-show-results): describe upset plots

Next, we explored the mechanisms linking the structures and the outcomes by analyzing regional disparity in influenced water use for each province by institutional shifts.
% 87-WAS 后各省响应的差异是理解制度影响机制的关键
Differences in provincial responses to 87-WAS are vital to understanding the mechanism of institutional shifts' impacts.
% 我们的结果表明，各省加速用水的比例（实际用水量超出模型预测用水量的比例）与各省黄河水取用量呈现显著正相关
Our results show that the proportion of accelerated water consumption in each province (the proportion of actual water consumption exceeding the predicted water consumption by the model) has a significant correlation to the Yellow River water consumption in each province (Figure~\ref{upset}A).
% 但明显的加速效应仅突出体现在主要用水省份上，对大多数省份来说，87-WAS 带来的影响并不大，
However, the apparent acceleration effect of the 87-WAS was only prominent in the significant water-using provinces (Neimeng, Henan, and Shandong), and there were no evident impacts for most provinces (Figure~\ref{upset}B).
% 尤其是常年超指标用水的山东与内蒙，分别在1987到1998年的十年间使用了高于模型预测值的xx%和xx%的用水量。
In particular, Shandong and Inner Mongolia, both provinces that exceeded the prescribed water uses of the 87-WAS, used xx\% and XX\% more water uses than predicted by the model from 1987 to 1998, respectively.
% 与黄河水取用量相比，各省对制度规定的分水配额的满意度（用各省实际分水与规划预期的差值表示）反而与这个加速效应的相关性并不显著。
On the contrary, the satisfaction of each province with the water allocation stipulated by the 87-WAS (expressed by the difference between the actual water allocation of each province and the expected planning value) is not significantly correlated with this acceleration effect.

@@

% 经济模型与理论解释
%! 这里可以指出他们过去的经济发展路径
We analyzed mathematically why the mismatched structure made win-wins holistically elusive in the institution shift of 87-WAS (\textit{method} and \textit{Supplementary Material S4}).
% 我们的模型表明，对于已经具有经济效率的用户来说，为了未来的经济增长而加速开采资源是由更大的边际收益引起的
Our model suggests that for users who are already economically efficient, greater marginal returns from water induce the acceleration of extracting resources for future economic growth (Figure~\ref{economic_model}).
% 因此，这种制度引发了一种与可持续用水意图背道而驰的激励扭曲。
Therefore, isolated stakeholders reacted variety to the similar marginal cost, and the institution of 87-WAS thus triggered an incentive distortion besides the initial intention of sustainable water use.
% 相反，中央管理(1998年以后的YRCC)能够有效降低边际生态成本
On the contrary, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs as stakeholders take corresponding responsibilities to the YRCC (\textit{Supplementary Material S4}).
% 制度结构和结果的差异呼应了SES成功治理的前景，通过间接(或垂直)在不同的利益相关者之间建立联系(在这种情况下是通过管理)
The alignments of differences in institutional structures and outcomes echo the hypothesis of successful governance in SES by indirectly (or vertically) creating links between different stakeholders (in the YRB cases, through administration).
%! citation

>>>>

Differences between stakeholders in responses to institutional shifts are vital to understanding the mechanism between structures and outcomes.
Our results show that the proportion of accelerated water use in each province after the decade of 87-WAS (the proportion of actual water use exceeding the predicted water use by the model) has a significant correlation ($p<0.05$, see \textbf{Methods}) to the Yellow River water use in each province (Figure~\ref{upset}A).
Furthermore, while no evident impacts for most provinces (no more than $10\%$ differences, the apparent acceleration effects were only prominent in the big water-using provinces (e.g., Neimeng, Henan, and Shandong. Figure~\ref{upset}B).
In particular, Neimeng and Shandong, both provinces that exceeded the prescribed water uses of the 87-WAS, used $44.25\%$ and $25.69\%$ more water uses than the prediction from 1987 to 1998, respectively.
Furthermore, the satisfaction of each province with the water allocation stipulated by the 87-WAS (expressed by the difference between the actual water allocation of each province and the expected planning value) is not significantly correlated with the acceleration.
By contrast, after the 98-UBR, with the exception of Shaanxi (which has always been abundant in water quota) had evident ($17.53\%$) increasd water use, almost all provinces have seen significant declines in water use ($-12.5\%$ on average).
Neither the satisfaction nor Yellow River water use, however, have correlation with the declines.

@@

% 经济模型与理论解释
%! 这里可以指出他们过去的经济发展路径
We analyzed mathematically why the mismatched structure made win-wins holistically elusive in the institution shift of 87-WAS (\textit{method} and \textit{Supplementary Material S4}).
Our model suggests that for users who are already economically efficient, greater marginal returns from water induce the acceleration of extracting resources for future economic growth (Figure~\ref{economic_model}).
Therefore, isolated stakeholders reacted variety to the similar marginal cost, and the institution of 87-WAS thus triggered an incentive distortion besides the initial intention of sustainable water use.
On the contrary, the presence of central management (by the YRCC in this case, after 1998) can effectively reduce marginal ecological costs as stakeholders take corresponding responsibilities to the YRCC (\textit{Supplementary Material S4}).
The alignments of differences in institutional structures and outcomes echo the hypothesis of successful governance in SES by indirectly (or vertically) creating links between different stakeholders (in the YRB cases, through administration).
%! citation

### 2022-04-06 docs/papers/01_manuscript/drafs.tex
docs(results2-section1-show-results): describe upset plots

>>>>

% 在我们的研究期间(从1975年到2008年)，机构在三种不同的结构之间转换:免费访问、87-WAS和98-UBR。
In our study period, the institution shifted between three different structures (Figure~\ref{structure} A to C).
% 长江水利委员会是长江流域的主要负责人，其任务是报告和分析1998年以前长江流域的用水量(87-WAS之后)。
However, the YRCC, whose primary official response to the river before 1998, the mandate was to conserve the riverway environment, construct and maintain infrastructures, and report on and analyze water consumption (after the 87-WAS) in the YRB, i.e., connecting the ecological nodes (different river reaches) horizontally ~\cite{wang2019a}.
